Local wind regime induced by giant linear dunes: comparison of ERA5-Land reanalysis with surface measurements

### 2022-07-13 Paper/main.tex
Splitting acknowledgements section

All data used in this study can be found in \citet{DataPaper}. Note that it contains modified Copernicus Climate Change Service Information (2021). Neither the European Commission nor ECMWF is responsible for any use that may be made of the Copernicus Information or Data it contains. Documented codes used in this study to analyse this data are available at https://github.com/Cgadal/GiantDunes (will be made public upon acceptance of this manuscript for publication).

Multiple grants have supported the collection of wind data through visits to the four sites between 2013 and 2020 (John Fell Oxford University Press (OUP) Research Fund (121/474); National Geographic (CP-029R-17); Natural Environment Research Council UK (NE/R010196/1 and NE/H021841/1 NSFGEO-NERC); Southampton Marine and Maritime Institute SMMI EPSRC-GCRF UK), along with research permits (1978/2014, 2140/2016, 2304/2017, 2308/2017, RPIV00022018, RPIV0052018, RPIV00230218).  The authors are very grateful for support from Etosha National Park (especially Shyane K\"otting, Boas Erckie, Pierre du Preez, Claudine Cloete, Immanuel Kapofi, Wilferd Versfeld, and Werner Kilian), Gobabeb Namib Research Institute (Gillian Maggs-K\"olling and Eugene Marais), The Skeleton Coast National Park (Joshua Kazeurua).  Various researchers and desert enthusiasts have assisted with instruments and the logistics of expeditions, especially Mary Seely for expert guidance at the North Sand Sea site.

Finally, we acknowledge financial support from the Laboratoire d'Excellence UnivEarthS Grant ANR-10-LABX-0023, the Initiative d'Excellence Universit\'e de Paris Grant ANR-18-IDEX-0001, the French National Research Agency Grants ANR-17-CE01-0014/SONO and the National Science Center of Poland Grant 2016/23/B/ST10/01700.

@@

>>>>

@@

{\footnotesize\noindent\textbf{Data Availability}~All data used in this study can be found in \citet{DataPaper}. Note that it contains modified Copernicus Climate Change Service Information (2021). Neither the European Commission nor ECMWF is responsible for any use that may be made of the Copernicus Information or Data it contains. Documented codes used in this study to analyse this data are available at https://github.com/Cgadal/GiantDunes (will be made public upon acceptance of this manuscript for publication).}

\vspace{.2cm }

{\footnotesize\noindent\textbf{Fundings}~Multiple grants have supported the collection of wind data through visits to the four sites between 2013 and 2020 (John Fell Oxford University Press (OUP) Research Fund (121/474); National Geographic (CP-029R-17); Natural Environment Research Council UK (NE/R010196/1 and NE/H021841/1 NSFGEO-NERC); Southampton Marine and Maritime Institute SMMI EPSRC-GCRF UK), along with research permits (1978/2014, 2140/2016, 2304/2017, 2308/2017, RPIV00022018, RPIV0052018, RPIV00230218).  The authors are very grateful for support from Etosha National Park (especially Shyane K\"otting, Boas Erckie, Pierre du Preez, Claudine Cloete, Immanuel Kapofi, Wilferd Versfeld, and Werner Kilian), Gobabeb Namib Research Institute (Gillian Maggs-K\"olling and Eugene Marais), The Skeleton Coast National Park (Joshua Kazeurua).  Various researchers and desert enthusiasts have assisted with instruments and the logistics of expeditions, especially Mary Seely for expert guidance at the North Sand Sea site.
%
Finally, we acknowledge financial support from the Laboratoire d'Excellence UnivEarthS Grant ANR-10-LABX-0023, the Initiative d'Excellence Universit\'e de Paris Grant ANR-18-IDEX-0001, the French National Research Agency Grants ANR-17-CE01-0014/SONO and the National Science Center of Poland Grant 2016/23/B/ST10/01700.}

\vspace{.2cm }
{\footnotesize\noindent\textbf{Conflict of interest}~All authors declare that they have no conflicts of interest.}
